Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Don't need 'current' when talking about why OpenGL 3
Diagram of clipping process for Boolean XOR

The two approaches were implemented using OpenGL with C++.  To ensure results
are relevant to current and future applications, we used only the core profile
of OpenGL 3.  In other words, no deprecated functionality from OpenGL 2 was
used.  Furthermore, because OpenGL 4 is a superset of the OpenGL 3 core profile,
the implementation will easily work with that as well.

@@

The Boolean operations required by the two approaches were implemented as two
separate nodes.  Currently both nodes take two cubes, which are assumed to be
axis-aligned.  {\tt BooleanAndNode} finds the intersection of the two cubes by
finding the minimums and maximums of the cubes in world space.  {\tt
BooleanXorNode} does the same, but then uses a variation of the well-known
Sutherland-Hodgman polyline-clipping algorithm to break up the cubes into pieces
around the intersection.  Both nodes use the {\tt NodeListener} interface to
only update their geometry when the cubes move.

>>>>

The two approaches were implemented using OpenGL with C++.  To ensure results
are relevant to future applications, we used only the core profile of OpenGL 3.
In other words, no deprecated functionality from OpenGL 2 was used.
Furthermore, because OpenGL 4 is a superset of the OpenGL 3 core profile, the
implementation will easily work with that as well.

@@

The Boolean operations required by the two approaches were implemented as two
separate nodes.  Currently both nodes take two cubes, which are assumed to be
axis-aligned.  {\tt BooleanAndNode} finds the intersection of the two cubes by
finding the minimums and maximums of the cubes in world space.  {\tt
BooleanXorNode} does the same, but then uses a variation of the well-known
Sutherland-Hodgman polyline-clipping algorithm to break up the cubes into pieces
around the intersection, as shown in figure \ref{clipping}.  Both nodes use the
{\tt NodeListener} interface to only update their geometry when the cubes move.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{clipping.pdf}
\caption{Variation of Sutherland-Hodgman clipping algorithm in Boolean XOR
implementation.}
\label{clipping}
\end{figure}
